Proposed Solution

### 2017-01-22 CAV17/secs/trans.tex
cav17: figure 2 caption
fixing type rules
use double colon for basic types

\begin{figure}[!htb]
    \caption{A learning set of configuration files}
    \centering
    \begin{minipage}{.25\textwidth}
	\begin{lstlisting} [label={lst:1.cnf},language=C,caption={1.cnf}]
[server]
foo = ON
[client]
bar = 1
	\end{lstlisting}
    \end{minipage}%
    \hspace{1cm}
    \begin{minipage}{0.25\textwidth}
	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={2.cnf}]
[server]
foo = ON
[client]
bar = ON
	\end{lstlisting}
    \end{minipage}
    \hspace{1cm}
    \begin{minipage}{0.25\textwidth}
	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={3.cnf}]
[server]
foo = OFF
[client]
bar = OFF
	\end{lstlisting}
    \end{minipage}
\end{figure}

@@

\begin{mathpar}
\hspace{-0.4cm} %no idea why, but this is better than \centering here
\inferrule* [Right=bool\_int]
{(k,v) \in C \\ v \in \{0,1\}}
{k:[int\pluseq 1,bool\pluseq 1]}
\and
\inferrule* [Right=eq\_rule]
{k1 : \tau \\ k2 : \tau \\ \tau \in \mathcal{T}}
{eq(k1,k2) : Rule}
\and
\inferrule* [Right=bool\_resolve]
{k:\tilde{\tau} \\ \tilde{\tau} \vdash bool \geq 2 \land \ast \leq 1}
{k : bool}
\and
\\
\inferrule* [Right=bool]
{(k,v) \in C \\ v \in \{ON,OFF\}}
{k:[bool\pluseq 1,string\pluseq 1]}
\end{mathpar}

In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $\in \tilde{\mathcal{T}}$ can be resolved to a basic type $\in \mathcal{T}$ with enough evidence.
The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other type.
While a user may implement overlapping inference rules, this are resolved by assigning the keyword a list of types.
This is then effectively a subtyping relation.

\begin{mathpar}
%\centering 
\inferrule* [Right=int\_resolve]
{k:[int \geq 1]}
{k : int}
\and
\\
\inferrule* [Right=int\_bool\_resolve]
{k:[bool \geq 2, \ast \leq 1] \\ k:[int \geq 1]}
{k : [bool,int]}
\end{mathpar}

>>>>

\begin{figure}[!htb]
    \centering
    \begin{minipage}{.25\textwidth}
	\begin{lstlisting} [label={lst:1.cnf},language=C,caption={1.cnf}]
[server]
foo = ON
[client]
bar = 1
	\end{lstlisting}
    \end{minipage}%
    \hspace{1cm}
    \begin{minipage}{0.25\textwidth}
	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={2.cnf}]
[server]
foo = ON
[client]
bar = ON
	\end{lstlisting}
    \end{minipage}
    \hspace{1cm}
    \begin{minipage}{0.25\textwidth}
	\begin{lstlisting} [label={lst:2.cnf},language=C,caption={3.cnf}]
[server]
foo = OFF
[client]
bar = OFF
	\end{lstlisting}
    \end{minipage}

    \caption{A learning set of configuration files}
\end{figure}

@@

\begin{mathpar}
\hspace{-0.4cm} %no idea why, but this is better than \centering here
\inferrule* [Right=bool\_int]
{(k,v) \in C \\ v \in \{0,1\}}
{k:[int\pluseq 1,bool\pluseq 1]}
\and
\inferrule* [Right=eq\_rule]
{k1 :: \tau \\ k2 :: \tau \\ \tau \in \mathcal{T}}
{eq(k1,k2) :: Rule}
\and
\inferrule* [Right=bool\_resolve]
{k:\tilde{\tau} \\ \tilde{\tau} \vdash bool \geq 2 \land \ast \leq 1}
{k :: bool}
\and
\\
\inferrule* [Right=bool]
{(k,v) \in C \\ v \in \{ON,OFF\}}
{k:[bool\pluseq 1,string\pluseq 1]}
\end{mathpar}

In the {\scriptsize BOOL\_RESOLVE} rule, a keyword with a probabilistic type $k : \tilde{\tau} \in \tilde{\mathcal{T}}$ can be resolved to a basic type (expressed with the double colon $ k :: \tau \in \mathcal{T}$) with enough evidence.
The definition of enough evidence must be empirically determined by the user depending on the quality of the learning set.
In this case, we allow a probabilistic type to resolve to a boolean if we have two counts for boolean, and no more than one count for any other type.

A user may implement overlapping inference rules, for example in {\scriptsize INT\_RESOLVE}.
This not a subtyping relation, as the predicates over the counts may not be strictly overlapping.
We simply allow the double colon (::) to type a single keyword in multiple ways.
Because the only typing judgments on a basic type are terminal, {\scriptsize EQ\_RULE}, there is no problem with ambiguity as we would have in a traditional lambda calculus that included function application.

\begin{mathpar}
%\centering 
\inferrule* [Right=int\_resolve]
{k:\tilde{\tau} \\ \tilde{\tau} \vdash int \geq 1}
{k :: int}
\end{mathpar}
